Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-11-09 paper/paper.tex
Search times
Progress?

\begin{abstract}
    Modern subgraph isomorphism solvers use strong value-ordering heuristics to direct search, but
    these heuristics are not perfect, particularly for early choices. Our results suggest that
    discrepancy-based searches are too expensive to be effective at offsetting this weakness.
    However, restarts with a random value-ordering heuristic beats conventional search with the best
    tailored heuristic. This motivates the introduction of a slightly-random value-ordering
    heuristic with similar behaviour to the tailored heuristic: when combined with restarts, this
    new heuristic is even more effective on satisfiable instances, whilst not significantly
    decreasing performance on unsatisfiable instances.
\end{abstract}

@@

We could try to introduce tiebreaking mechanisms to further refine this heuristic. However, given
the extreme cost of making an incorrect branching choice early on in search, we believe it is more
fruitful to investigate alternatives to simple backtracking (depth-first) search. This paper
evaluates two such approaches: discrepancy search (which perform poorly), and restarts (which are
extremely beneficial). To make restarts work, we introduce a new value-ordering heuristic, which is
nearly the same as ``highest degree first'' except with small amounts of heavily biased randomness.
The effects of the changes we propose are shown in the top plot of \cref{figure:scatter}: we can
make a state-of-the-art algorithm perform much better on a large number of satisfiable instances,
without substantially degrading its performance on unsatisfiable or the remaining satisfiable
instances.

?? And concludes what?

@@

?? Other studies use a random selection of 200 of each of the mesh and images instances
\citep{DBLP:journals/cviu/DamiandSHJS11}, partly because some earlier solvers find many of these
instances extremely hard, and partly to avoid skewing a portfolio. We want larger numbers of
satisfiable instances, so we include all pattern / target pairs. This gives a total of 14,621
instances, ?? of which we know are satisfiable, and ??  unsatisfiable.

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-value-ordering-heuristics.pdf}

@@

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-heuristics.pdf}

@@

\subsection{Discrepancies Don't Help}

?? Code up LDS and DDS and the like properly, and plot them being disappointing here.

@@

    \caption{Cumulative number of instances solved over time, with (dotted lines) and without (solid
    lines) restarts.}
    \label{figure:restarts}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-nogoods.pdf}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-overheads.pdf}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-restart-policies.pdf}

@@

\section{Other Subgraph Solvers}

?? Also do this in McSplit and kdown?

@@

>>>>

\begin{abstract}
    Modern subgraph isomorphism solvers use value-ordering heuristics to direct search, but these
    heuristics are not perfect, particularly for early choices. We investigate discrepancy searches
    and restarts to offset this weakness. Our results suggest that discrepancy-based searches are
    too expensive to be effective.  However, restarts with a random value-ordering heuristic beats
    conventional search with the best tailored heuristic. This motivates the introduction of a
    slightly-random value-ordering heuristic with similar behaviour to the tailored heuristic: when
    combined with restarts, this new heuristic is even more effective on satisfiable instances,
    whilst not significantly decreasing performance on unsatisfiable instances.
\end{abstract}

@@

We could try to introduce tiebreaking mechanisms to further refine this heuristic. However, given
the extreme cost of making an incorrect branching choice early on in search, we believe it is more
fruitful to investigate alternatives to simple backtracking (depth-first) search. This paper
evaluates two such approaches: discrepancy search (which perform poorly), and restarts (which are
extremely beneficial). To make restarts work, we introduce a new value-ordering heuristic, which is
nearly the same as ``highest degree first'' except with small amounts of heavily biased randomness.
The effects of the changes we propose are shown in \cref{figure:scatter}: we can make a
state-of-the-art algorithm perform much better on a large number of satisfiable instances, without
substantially degrading its performance on unsatisfiable instances.

@@

?? Other studies use a random selection of 200 of each of the mesh and images instances
\citep{DBLP:journals/cviu/DamiandSHJS11}, partly because some earlier solvers find many of these
instances extremely hard, and partly to avoid skewing a portfolio. We want larger numbers of
satisfiable instances, so we include all pattern / target pairs. This gives a total of 14,621
instances, at least 2,110 of which are known to be satisfiable, and at least 12,323 are
unsatisfiable.

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-value-ordering-heuristics.pdf}

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-heuristics.pdf}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-dds.pdf}

    \caption{The effects of using depth-bounded discrepancy search.}\label{figure:dds}
\end{figure}

@@

@@

?? \cref{figure:dds}. Sometimes extremely beneficial on satisfiable instances. However, on both
unsatisfiable and satisfiable instances, the overheads are often large, and the algorithm is not
better in aggregate (even when only considering satisfiable instances).

@@

    \caption{Cumulative number of instances solved over time, with (dotted lines) and without (solid
    lines) restarts, and with depth-bounded discrepancy search (dashed line).}
    \label{figure:restarts}
\end{figure}

@@

@@

@@

\appendix
\clearpage
\section{Further Experiments}

A bit of text here.

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-scatter-nogoods.pdf}

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-scatter-overheads.pdf}

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-restart-policies.pdf}
